Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Successfully merged the retro diagnosis and ethnicity graphs

retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")

@@

#####Plot Style 1

@@

@@

ggarrange(retro_diagnosis_plot, retro_ethnicity_plot,
         labels = c(""),
         ncol = 2, nrow = 1)

>>>>

retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "")

@@

####Plot diagnosis

@@

Note: I'm modifying the original retro plots to make them easier to merge together

@@

#Note: Adding the data labels makes the graph look messy

arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())# +
#  geom_text(aes(label = n),
#            size = 3,
#            position = position_dodge(width=0.9), 
#            vjust=-0.25)

#Graph 2
arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, 
                                 vjust = 0.5,
                                 size = 8)) +
  theme(legend.position = "none") + 
  #theme(legend.title = element_blank()) +
  #geom_text(aes(label = n),
  #          size = 3,
  #          position = position_dodge(width=0.9), 
  #          vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))

arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")

ggarrange(retro_diagnosis_plot, arranged_retro_ethnicity_plot,
          common.legend = TRUE)
